### 2016-11-13 thesis/intro/intro.tex
tmp commit

\noindent
When any one of these neurons, neuropeptides, hormones or its corresponding receptors become defective, it can lead to some form of eating disorder.
Therefore the roles of these neurons, neuropeptides, and hormones are crucial for healthy diet and body weight maintenance.

@@

In close relation to this mutation is the mutation in the leptin receptor gene.
\citet{Clement1998} have discovered a single nucleotide substitution mutation that led to the leptin receptor transcript that skipped exon 16 -- leading to a form of the receptor with no transmembrane or intracellular domain.
Individuals with this rare mutation showed extreme hyperphagia and symptoms of early-onset obesity, even though their circulating leptin levels were present abundantly \citep{Clement1998}.

\citep{Jackson1997}
\citep{Krude1998}
\\

\citep{Farooqi2003}
\citep{Kublaoui2006}
\citep{Dubern2001}
\citep{Challis2002}
\\

\noindent
Polygenic obesity is where 
\\

@@

Talk about all the mutations and contribution of these genes to obesity, and then link it back to ``thrifty'' gene
\citep{Neel1962}

>>>>

\noindent
When any one of these neurons, neuropeptides, hormones or its corresponding receptors become defective, it can lead to some form of eating disorder (briefly covered in \cref{ssub:Individual-level_(micro-level)_factors}: \nameref{ssub:Individual-level_(micro-level)_factors}).
Therefore the roles of these neurons, neuropeptides, and hormones are crucial for healthy diet and body weight maintenance.

@@

In close relation to this mutation is the mutation in the leptin receptor gene.
\citet{Clement1998} have discovered a single nucleotide substitution mutation that led to the leptin receptor transcript that skipped exon 16, leading to a form of the receptor with no transmembrane or intracellular domain.
Individuals with this rare mutation showed extreme hyperphagia and symptoms of early-onset obesity, even though their circulating leptin levels were present abundantly \citep{Clement1998}.

The next couple of mutations are associated with the synthesis and the processing of \gls{pomc}.
\citet{Krude1998} found single nucleotide mutations in the exonic region of the \gls{pomc} gene that affected the transcription of the $\alpha$-\gls{msh} region (and some other regions) of \gls{pomc}.
\citet{Jackson1997} identified a mutation in the \gls{pc1}, an enzyme responsible for the processing of many prohormones and neuropeptides, including \gls{pomc}.
In either case, the mutation resulted in the lack of $\alpha$-\gls{msh} in the neurons for satiety signalling and caused severe early-onset obesity.

As mentioned earlier, even though these mutations are very rare and affects only those individuals that have one of these mutations, it had a profound impact in the field of obesity research and contributed significantly to the knowledge of the mechanism of how obesity develops.
\\

% \citep{Farooqi2003}
% \citep{Kublaoui2006}
% \citep{Dubern2001}
% \citep{Challis2002}
% \\

\noindent
Polygenic obesity is where a combination of variants in multiple genes or multiple regions of the genome, together with environmental factors, causes obesity in the individual \citep{Moustafa2013}.
Unlike in monogenic obesity where a single mutation in a gene causes severe obesity, the variants in some of the genes or genomic regions involved in polygenic obesity have little effect on the individual's obesity status by itself, but in combination with many other variants, together with environmental factors, it has a serious effect on the individual.

Known as the ``thrifty gene'' hypothesis, \citet{Neel1962} suggested that these genes that were important in obesity have been around in the population for many generations, as it would have had a selective advantage in an environment where the population experienced starvation more frequently than the current generation.
However, as food became more accessible, a subset of the population who were particularly good at storing fat and survive the starvation period ``overreacted'' to this rapid change in the environment \citep{Bell2005, Spiegelman2001}.
These observations in the rise in obesity in subsets of population cannot be explained simply by external factors alone, and there is a significant genetic component involved \citep{Bell2005}.
\\

@@
